---
title: "My awesome report"
author: "Claudiu Forgaci"
output: html_document
---

```{r setup}
# Load packages
library(here)
library(tidyverse)
```

```{r load-data}
# Load data
path <- here("data", "gapminderDataFiveYear.tsv")
gapMinder <- read.delim(path)
```

# Heading

## Sub-heading

Text...

### Sub-heading

Text...

# Introduction

<!-- This is a note -->

This paper uses the **tidyverse** package along with the *gapminder* dataset, which contains the columns:

1.  country

-   Name of country

2.  year

-   Year of observation

3.  pop

-   Population of country

4.  continent

-   Continent where the country is located

5.  lifeExp

-   Life expectancy

6.  gdpPercap

-   GDP per capita

## Insert table

The average GDP per capita grouped by `continent`.

```{r}
gapMinder |> 
  group_by(continent) |> 
  summarise(mean_gdpPercap = mean(gdpPercap)) |> 
  knitr::kable(caption = "We can also add a caption",
               col.names = c("Continent", "Mean GDP per Capita"))
```

## Inline R code

```{r}
cont <- "Europe"
mean_continent <- gapMinder |> 
  group_by(continent) |> 
  summarise(mean_lifeExp = mean(lifeExp)) |> 
  filter(continent == cont)
```

The average life expectancy in `r cont` is `r mean_continent`

